Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-11-01 Paper.Rmd
minor format adjustments

```{r IV-Hist-Exp, fig.cap="Distribution of the Helpfulness of Experience Goods"}
movies_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = NULL)
```

@@

p2 <- search_goods %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = "loess", color = "steelblue")+
  labs(x = "Review Rating")

@@

p2 <- movies_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 10)+
  labs(x = "Review Rating")

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Number of the Words")

p1_log <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 8)+
  labs(y = NULL, x = "log10(Number of the Words)")

p2 <- search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(x = "Number of the Words")

p2_log <- search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_log10(n.breaks = 8)+
  labs(x = "log10(Number of the Words)")

@@

```{r Experience-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Number of the Words")

p1_log <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 8)+
  labs(y = NULL, x = "log10(Number of the Words)")

p2 <- movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(x = "Number of the Words")

p2_log <- movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_log10(n.breaks = 8)+
  labs(x = "log10(Number of the Words)")

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Freshness of Review")

p1_log <- search_goods %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 8)+
  labs(y = NULL, x = "log10(Freshness of Review + 1)")

p2 <- search_goods %>% 
  ggplot(aes(Freshness, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(x = "Freshness of Review")

p2_log <- search_goods %>% 
  ggplot(aes(Freshness + 1, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_log10(n.breaks = 8)+
  labs(x = "log10(Freshness of Review + 1)")

@@

```{r Experience-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = "Freshness of Review")

p1_log <- movies_data %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 8)+
  labs(y = NULL, x = "log10(Freshness of Review + 1)")

p2 <- movies_data %>% 
  ggplot(aes(Freshness, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(x = "Freshness of Review")

p2_log <- movies_data %>% 
  ggplot(aes(Freshness + 1, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_log10(n.breaks = 8)+
  labs(x = "log10(Freshness of Review + 1)")

@@

p2 <- search_goods %>% 
  ggplot(aes(negative, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")

@@

p2 <- movies_data %>% 
  ggplot(aes(negative, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")

@@

```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

p2 <- search_goods %>% 
  ggplot(aes(positive, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")

@@

```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = NULL, x = NULL)

p2 <- movies_data %>% 
  ggplot(aes(positive, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue")+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")

@@

Total Votes is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].

@@

Tobit regression results are presented at Table \@ref(tab:Reg-Results) alongside with OLS results as a benchmark [@mudambi2010; @kuan2015; @choi2020].

@@

```{r Reg-Results, results='asis'}

stargazer(list("Search Tobit" = search_tobit,
               "Experience Tobit" = experience_tobit,
               "Search Linear" = search_lm,
               "Experience Linear" = experience_lm),
          type = "latex",
          notes.align = "l",
          header = FALSE,
          model.numbers = FALSE,
          column.labels = c("Search", "Experience", "Search", "Experience"),
          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
                               "log10(Total Vote)", "log10(Freshness + 1)",
                               "Positive Proportion",  
                               "Negative Proportion", "Rating x Review Length"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          label = "tab:Reg-Results")
```

@@

One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for movie reviews. For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word. One or more movies in the sample include movies where "Nicholas *Cage*" had the starring role. There are also "*Marvel* Cinematic Universe" movies present in the data. Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon. To test this problem words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types. Neither coefficient signs nor coefficient significances were changed. However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly. Further filtering was not pursued because of potential dangers of hypothesis fishing. (The results in Table \@ref(tab:Reg-Results) are the results with the filter.)

>>>>

```{r IV-Hist-Exp, fig.cap="Distribution of the Helpfulness of Experience Goods"}
movies_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 10)+
  labs(y = "Count")
```

@@

p2 <- search_goods %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(method = "loess", color = "steelblue", size = 1.7)+
  labs(x = "Review Rating")

@@

p2 <- movies_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 10)+
  labs(x = "Review Rating")

@@

```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Number of the Words")

p1_log <- search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 8)+
  labs(y = "Count", x = "log10(Number of the Words)")

p2 <- search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 8)+
  labs(x = "Number of the Words")

p2_log <- search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 8)+
  labs(x = "log10(Number of the Words)")

@@

```{r Experience-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Number of the Words")

p1_log <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Number of the Words)")

p2 <- movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 7)+
  labs(x = "Number of the Words")

p2_log <- movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 7)+
  labs(x = "log10(Number of the Words)")

@@

```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- search_goods %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

p2 <- search_goods %>% 
  ggplot(aes(Freshness, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 7)+
  labs(x = "Freshness of Review")

p2_log <- search_goods %>% 
  ggplot(aes(Freshness + 1, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 7)+
  labs(x = "log10(Freshness of Review + 1)")

@@

```{r Experience-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Freshness))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 6)+
  labs(y = "Count", x = "Freshness of Review")

p1_log <- movies_data %>% 
  ggplot(aes(Freshness + 1))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Freshness of Review + 1)")

p2 <- movies_data %>% 
  ggplot(aes(Freshness, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 6)+
  labs(x = "Freshness of Review")

p2_log <- movies_data %>% 
  ggplot(aes(Freshness + 1, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 6)+
  labs(x = "log10(Freshness of Review + 1)")

@@

p2 <- search_goods %>% 
  ggplot(aes(negative, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")

@@

p2 <- movies_data %>% 
  ggplot(aes(negative, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")

@@

```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
p1 <- search_goods %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Positive Words)")

p2 <- search_goods %>% 
  ggplot(aes(positive, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")

@@

```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
p1 <- movies_data %>% 
  ggplot(aes(positive))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Count", x = "Log10(Proportion of Positive Words)")

p2 <- movies_data %>% 
  ggplot(aes(positive, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 8)+
  labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")

@@

The number of Total Votes is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].

From Figures \@ref(fig:Search-Total) (B) and \@ref(fig:Experience-Total) (B) it can be observed that logarithmic transformation scales the variable in a better way for both good types. This is also good for linear models. Distributions for both good types are looking similar. There is a little difference though. Movies got voted many more times than search goods. This makes sense because relatively older movies are present in the data. In the case of electronics, it is hard to find reviews for older devices because they are not sold anymore so it is impossible to vote on them. This explains why there are so few amount of highly voted reviews for search goods.

```{r Search-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Search Goods and respective logarithmic transformations (B), (D)"}
p1 <- search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Total Vote")

p1_log <- search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
  scale_x_log10(n.break = 7)+
  labs(y = "Count", x = "log10(Total Vote)")

p2 <- search_goods %>% 
  ggplot(aes(Total_Vote, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 7)+
  labs(x = "Total Vote")

p2_log <- search_goods %>% 
  ggplot(aes(Total_Vote, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 7)+
  labs(x = "log10(Total Vote)")

On Figures \@ref(fig:Search-Total) (C) and (D) the smoother line may look like a straight horizontal line because the plot is small but there exist a weak negative slope. This might indicate two things. There is no association between these two variables or there is a negative relationship.

Figure \@ref(fig:Experience-Total) (C) and (D) show a different story. Figures might indicate that there is a positive relationship between these two variables.

Nonetheless, it should be noted that the variable Total Votes is the denominator part of the dependent variable Perceived Helpfulness so any interpretations to these plots should be done with care.

```{r Experience-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Experience Goods and respective logarithmic transformations (B), (D)"}
p1 <- movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
  scale_x_continuous(n.breaks = 7)+
  labs(y = "Count", x = "Total Vote")

p1_log <- movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
  scale_x_log10(n.break = 6)+
  labs(y = "Count", x = "log10(Total Vote)")

p2 <- movies_data %>% 
  ggplot(aes(Total_Vote, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_continuous(n.breaks = 7)+
  labs(x = "Total Vote")

p2_log <- movies_data %>% 
  ggplot(aes(Total_Vote, Helpfulness))+
  geom_point(alpha = 0.1)+
  geom_smooth(color = "steelblue", size = 1.7)+
  scale_x_log10(n.breaks = 6)+
  labs(x = "log10(Total Vote)")

@@

Tobit regression results are presented at Table \@ref(tab:Reg-Results-Tobit) alongside with OLS results as a benchmark at Table \@ref(tab:Reg-Results-OLS) [@mudambi2010; @kuan2015; @choi2020].

@@

```{r Reg-Results-Tobit, results='asis'}

stargazer(list("Search Tobit" = search_tobit,
               "Experience Tobit" = experience_tobit),
          type = "latex",
          notes.align = "l",
          header = FALSE,
          model.numbers = FALSE,
          column.labels = c("Search", "Experience"),
          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
                               "log10(Total Vote)", "log10(Freshness + 1)",
                               "Positive Proportion",  
                               "Negative Proportion", "Rating x Review Length"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          label = "tab:Reg-Results-Tobit",
          title = "Tobit Regression Results")
```

```{r Reg-Results-OLS, results='asis'}

stargazer(list("Search Linear" = search_lm,
               "Experience Linear" = experience_lm),
          type = "latex",
          notes.align = "l",
          header = FALSE,
          model.numbers = FALSE,
          column.labels = c("Search", "Experience"),
          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
                               "log10(Total Vote)", "log10(Freshness + 1)",
                               "Positive Proportion",  
                               "Negative Proportion", "Rating x Review Length"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          label = "tab:Reg-Results-OLS",
          title = "OLS Regression Results")
```

@@

One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for movie reviews. For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word. One or more movies in the sample include movies where "Nicholas *Cage*" had the starring role. There are also "*Marvel* Cinematic Universe" movies present in the data. Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon. To test this problem words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types. Neither coefficient signs nor coefficient significances were changed. However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly. Further filtering was not pursued because of potential dangers of hypothesis fishing. (The results in Tables \@ref(tab:Reg-Results-Tobit) and \@ref(tab:Reg-Results-OLS) are the results with the filter.)
